---
title: "Question 10"
author: "Joe Mitchell"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
m1 <- aov(formula = count ~ spray, 
          data = InsectSprays)
```
The overall effect of spray does appear to explain the variation in count (1-way ANOVA: F = 34.7, df = 5,66, P <0.001)

```{r}
boxplot(count ~ spray,  # create boxplot of count as a function of spray
        data = InsectSprays,
        xlab = "Spray",
        ylab = "Insect Count",
        main = "Insect Count by Spray")
abline(h = mean(InsectSprays$count),  # add overall mean line to boxplot
                lty = 2,
                lwd = 2,
                col = "red")

hist(residuals(m1), prob = TRUE,  # create histogram of density of residuals from ANOVA
     main = "Residuals of 1-Way ANOVA of \ncount ~ spray from InsectSprays")
curve(dnorm(x, mean = mean(residuals(m1)), sd = sd(residuals(m1))), add = TRUE, col = "red") # Add curve of what Gaussian Residuals would be
lines(density(residuals(m1)), col = "blue", lty = 3)  # add curve of test residuals
legend(x =1, y = 0.15,  # add legend labeling lines
       legend = c("Gaussain", "Residuals Density"),
       lty = c(1,3),
       col = c("red", "blue"))
```
Near the mean the residual density is higher than expected under Gaussian.
Our residuals at +2 to +4 are a lot lower than would be expected.
-7 to -10 and +7 to +10 are higher than we would expect. 
The distribution is mostly symmetrical around the mean.
There is a left skew to the histogram. 
This suggests that the residuals don't follow a Gaussian distribution

```{r}
library(car)
qqPlot(x = m1,
       main = "qqPlot of 1-way ANOVA residuals") # Generate qqplot of residuals of 1-way ANOVA
```
There are quite a few point that veer off the line in the qqplot, especially between -1 to -0.25 and +0.25 and +1
 This suggests that they don't follow a Gaussian distribution

```{r}
shapiro.test(residuals(m1)) 
```
This test provides evidence to support the above graphs evidence that the the
residuals of the 1 way ANOVA violate our assumption of Gaussian residual distribution
(Shapiro-Wilk: W = 0.96, p = 0.02)
